---
knit: (function(inputFile, encoding) {
      rmarkdown::render(inputFile, 
                        encoding = encoding, 
                        output_dir = here::here("output_pdf")) }) 
output:
  bookdown::pdf_book:
    highlight: pygments
    toc: true
    toc_depth: 2
    lot: true
    keep_tex: true
    number_sections: no
    fig_height : 5
    fig_width : 8
    includes:
      # in_header: ../tex_files/import.sty 
      before_body: ../tex_files/title.sty
documentclass: article
classoption: oneside
geometry: [top=1in, bottom=1in, right=1.1in, left=1.1in]
linestretch: 1.25
fontsize: 12pt
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```

\clearpage

```{r analysis-setup}

## ------- package setup ------------------------

library(dplyr)
library(purrr)
library(knitr)
library(broom)
library(tableone)
library(kableExtra)
library(equatiomatic)


## ------- data setup ------------------------

load(here::here("data", "wcgs.Rdata"))
sid <- 011
set.seed(sid)
mydat <- sample_n(wcgs, size = n(), replace = TRUE)


## ------- utility functions ------------------------

kab_tab <- function(tab, ...) {
  knitr::kable(tab,
               format = "latex",
               booktabs = TRUE,
               digits = 3,
               ...)
}

p_format <- function(pval) {
  ifelse(pval < .001, "<.001", as.character(round(pval, 3)))
}

mod_tab <- function(mod, ...) {
  mod %>%
    tidy() %>%
    mutate(p.value = p_format(p.value)) %>%
    kab_tab(align = "lrrrr",
            caption = "Estimate of Model Parameters", ...) %>%
    kable_styling(latex_options = "HOLD_position")
}

reg_eq <- function(mod, ref, ...) {
  extract_eq(mod,
             use_coefs = TRUE,
             intercept = "beta",
             wrap = TRUE,
             label = paste0("eq",ref),
             ...)
}

params <- function(mod, param, dec = 2) {
  round(mod$coefficients[[param]], dec)
}

```

# Answers to Questions
## Question 01
**Answer:** For the continuous variables `age` and `bmi`, mean and standard deviation (SD) is obtained. And for categorical variable `arcus`, `behpat`, and `chd69`, frequency and proportion (in percentage) is obtained as descriptive statistics, which are shown in the following table:

```{r Table-01}

## ------- Code for Question-01 ------------------------

tab <- CreateTableOne(
  data = mydat,
  vars = c("age", "bmi", "arcus", "behpat", "chd69"),
  factorVars = "arcus",
  addOverall = TRUE
)

tab_p <- print(tab, showAllLevels = TRUE, printToggle = FALSE)

kab_tab(tab_p, caption = "Descriptive Statistics") %>%
  kable_styling(latex_options = "HOLD_position")

```

\clearpage

## Question 02
**Answer:** 

#### Effect of age and bmi:
To check whether each of `age` and `bmi` has significant effect on `chol`, we need to do correlation test (pearson).

For each correlation test of `age` and `bmi` with `chol`, the hypotheses are,
\begin{align*}
H_o&: \rho = 0 \\
H_a&: \rho \neq 0
\end{align*}
where $\rho$ is the population correlation coefficient.

The appropriate test statistic for testing the hypothesis is,

$$
t_o = \frac{r\sqrt{n-2}}{\sqrt{1-r^2}}
$$

where $r$ is the sample correlation coefficient and $t_o$ follows $t_{n-2}$ 
distribution under $H_o$.

Here we will reject $H_o$ if the associated `p.value` is less then  $\alpha = 0.05$, where $\alpha$ is the level of significance.

Now from Table: \@ref(tab:Table-02), we can see that both of the variables `age` and `bmi`
is significantly associated with `chol` variable.

```{r Table-02}

## ------- Code for Question-02 ------------------------

arcus <- t.test(chol ~ arcus, data = mydat) %>%
  tidy() %>%
  mutate(term = "arcus") %>%
  select(term, estimate, statistic, p.value)

mydat %>%
  select(age, bmi) %>%
  map(~ cor.test(x = .x, y = mydat$chol)) %>%
  map_dfr(broom::tidy, .id = "term") %>%
  select(term:p.value) %>%
  bind_rows(arcus) %>%
  mutate(p.value = p_format(p.value)) %>%
  kab_tab(align = "lrrr",
          caption = "Correlation Test (age, bmi) and T-test (arcus) with chol") %>%
  kable_styling(latex_options = "HOLD_position")

```

#### Effect of arcus:
Now to check the effect of `arcus` (a categorical variable with level 0 and 1) on `chol`, we can do two sample t-test, where one sample is people with `arcus` 0 and 
other sample is people with `arcus` 1. Therefore, $\mu_o$ and $\mu_1$ are the 
population mean of arcus 0 and arcus 1 group respectively. 

Then our hypotheses are:
\begin{align*}
H_o&: \mu_o = \mu_1 \\
H_a&: \mu_o \neq \mu_1
\end{align*}
and appropriate test statistic (assuming unequal variance),

$$
t_o = \frac{\bar{x_o} - \bar{x_1}}{\sqrt{\frac{s_o^2}{n_o} + \frac{s_1^2}{n_1}}}
$$

where $\bar{x}$ and $s^2$ denotes sample mean and sample variance with subscript 
0 and 1 for `arcus` group 0 and 1 respectively and $n_o$ and $n_1$ are the corresponding sample sizes.

Here we will reject $H_o$ if the associated `p.value` is less then  $\alpha = 0.05$, where $\alpha$ is the level of significance.

Then from Table: \@ref(tab:Table-02), since `p.value` is less than 0.001 we can conclude that mean `chol` differs significantly for 0 and 1 group of `arcus`, that is, `arcus` has significant effect on `chol`.

#### Effect of behpat:

To check the effect of `behpat` on `chol`, we can do oneway ANOVA. In this case the hypotheses are:
\begin{align*}
H_o&: \mu_1 = \mu_2 \\
H_a&: \mu_i \neq \mu_j \! &\text{for at least one i $\ne$ j}
\end{align*}
and test statistic is $F_o = \frac{MS_{reg}}{MS_{E}}$. We will reject $H_o$ if associated `p.value` is less than 0.05.

```{r Table-03}

anova(lm(chol ~ behpat, data = mydat)) %>%
  tidy() %>%
  mutate(p.value = p_format(p.value)) %>%
  kab_tab(align = "lrrrrr",
          caption = "One Way Analysis of Variance for chol on behpat") %>%
  kable_styling(latex_options = "HOLD_position")

```

Then from Table: \@ref(tab:Table-03), we conclude that mean `chol` differs significantly over the levels of `behpat`.

\clearpage

## Question 03

**Answer:** To examine the association between `behpat`  and `chd69`, the hypotheses are:
\begin{align*}
H_o&: \text{There's no association between \texttt{behpat} and \texttt{chd69}.} \\
H_a&: \text{There's association between \texttt{behpat} and \texttt{chd69}.}
\end{align*}
Here, the test statistics is:
$$
\chi^2 = \sum_{i=1}^{r}\sum_{j=1}^{c}\frac{(O_{ij} - E_{ij})^2}{E_{ij}}
$$
Where, $O_{ij}$ is observed frequency and $E_{ij}$ is the expected frequency and $r$, $c$ is the row and column number of contingency table \ref{Table-04}

Here, we would reject $H_o$ if associated `p.value` corresponding to test statistics
is less the 0.05.

```{r Table-04-05}

## ------- Code for Question-03 ------------------------

df_cont <- mydat %>% janitor::tabyl(behpat, chd69)

tab_cont <- df_cont %>%
  kab_tab() %>%
  add_header_above(header = c(" " = 1, "CHD" = 2))

tab_chi <- df_cont %>%
  janitor::chisq.test() %>%
  tidy() %>%
  select(statistic, p.value) %>%
  mutate(p.value = p_format(p.value)) %>%
  kab_tab()

tab_side <- c(
    "\\begin{table}[H]
      \\begin{minipage}{.5\\linewidth}
      \\centering",
      tab_cont,
      "\\caption{Contingency table}
      \\label{Table-04}
    \\end{minipage}%
      \\begin{minipage}{.5\\linewidth}
        \\centering",
    tab_chi,
    "\\caption{chi-square test}
    \\label{Table-05}
    \\end{minipage}
      \\end{table}"
  )
```

`r paste0(tab_side, collapse="")`

Now from the Table \ref{Table-05}, since `p.value` is less than 0.001, we can conclude that there's a significant association between `behpat` and `chd69`.

\clearpage

## Question 04
**Answer:** 
```{r Table-06}

## ------- Code for Question-04 ------------------------

m1 <- lm(chol ~ age, data = mydat)
m1 %>% mod_tab()

```

The fitted regression line is:
```{r eq01}
reg_eq(m1, 1)
```
Then, the cholesterol level is expected to increase by `r params(m1, 2)` unit
for 1-year increase of age.


## Question 05
**Answer:** 
```{r Table-07}

## ------- Code for Question-05 ------------------------

m2 <- lm(chol ~ dibpat, data = mydat)
m2 %>% mod_tab()

```

The fitted regression line is:
```{r eq02}
reg_eq(m2, 2)
```
So, we can say that, Mean cholesterol level of `Type A dibpat` subjects is `r params(m2, 1)`. Also, mean cholesterol level of `Type A dibpat` subjects is `r -params(m2, 2)` unit higher than `Type B dibpat` subjects.

\clearpage

## Question 06
**Answer:** 
```{r Table-08}

## ------- Code for Question-05 ------------------------

m3 <- lm(chol ~ behpat, data = mydat)
m3 %>% mod_tab()

```
The fitted regression line is:

```{r eq03}
reg_eq(m3, 3)
```
So, we can say, since `Type A1` Behavior pattern subjects are reference group,

* Mean cholesterol level of `Type A1` subjects is `r params(m3, 1)` unit.
* Mean cholesterol level of `Type A2` subjects is `r -params(m3, 2)` unit         lower than that of `Type A1` subjects.
* Mean cholesterol level of `Type B3` subjects is `r -params(m3, 3)` unit         lower than that of `Type A1` subjects.
* Mean cholesterol level of `Type B4` subjects is `r -params(m3, 4)` unit         lower than that of `Type A1` subjects.


## Question 07
**Answer:** 
```{r Table-09}

## ------- Code for Question-08 ------------------------

m4 <- lm(chol ~ age + dibpat, data = mydat)
m4 %>% mod_tab()

```
The fitted regression line is:

```{r eq04}
reg_eq(m4, 4)
```
Since `Type A1` subjects are reference group,

* Mean cholesterol level of subjects with age 0 and `Type A` pattern is `r   params(m4, 1)` unit.
* Mean cholesterol level increases about `r params(m4, 2)` for 1-year increase    of age, holding dibpat fixed.
* Mean cholesterol level of `Type B2` subjects is `r -params(m4, 3)` unit lower than that of `Type A` dibpat subjects, holding the subject's age fixed.

Here, Both the regression coefficients corresponding to age and dibpat (Eq \ref{eq: eq4}) have changed from the case of simple linear regression in Eq \ref{eq: eq1} and Eq \ref{eq: eq2}. And also the value of $R^2_{adj}$ increased.


## Question 08
**Answer:** 
```{r Table-10}

## ------- Code for Question-08 ------------------------

mydat %>%
  mutate(age40 = age - 40) %>%
  lm(chol ~ age40, data = .) -> m5

m5 %>% mod_tab()

```

The new fitted model after subtracting 40 from the variable `age` is:
```{r eq05}
reg_eq(m5, 5)
```

* Since the explanatory variable is age minus 40, we can say, the mean cholesterol    level of a 40 year old subject is `r params(m5, 1)`.
* Mean cholesterol level is expected to in increase by `r params(m5, 2)` for 1 year   increase of age.

The main difference of this model (Eq \ref{eq: eq1}) compared to model \ref{eq: eq5} is that, we can interpret the intercept term for this model logically.

## Question 09
**Answer:** 
```{r Table-11}
## ------- Code for Question-08 ------------------------

m6 <- lm(chol ~ dibpat * smoke, data = mydat)
m6 %>% mod_tab()
```

In this case, the fitted model is:
```{r eq06}
reg_eq(m6, 6)
```

Here the reference groups are `Non-smoker` and dibpat `Type A` subjects. So,

* The mean cholesterol level of Type A non smoker subject is `r params(m6, 1)` unit.
* Among the non-smokers, mean cholesterol level of dibpat `Type B` subjects is `r -params(m6, 2)` unit lower compared to `Type A` subject.
* Among the `Type A` subjects, mean cholesterol level of smokers is `r params(m6, 3)` unit higher than that of non-smokers.
* Difference of mean cholesterol level between smokers and non-smokers is `r params(m6, 4)` unit higher in `Type B` dibpat subjects compared to that of `Type A` dibpat subjects.

\clearpage

# R-code
```{r show-code, ref.label=all_labels(), echo = TRUE, eval=FALSE}

```
