## Answer To Ques 02

#### Effect of age and bmi : 
To check whether each of `age` and `bmi` has significant effect on `chol`, we need to do correlation test (pearson).

For each correlation test of `age` and `bmi` with `chol`, the hypotheses are,
\begin{align*}
H_o&: \rho = 0 \\
H_a&: \rho \neq 0
\end{align*}
where $\rho$ is the population correlation coefficient.

The appropriate test statistic for testing the hypothesis is,

$$
t_o = \frac{r\sqrt{n-2}}{\sqrt{1-r^2}}
$$

where $r$ is the sample correlation coefficient and $t_o$ follows $t_{n-2}$ 
distribution under $H_o$.

Here we will reject $H_o$ if the associated `p.value` is less then  $\alpha = 0.05$, where $\alpha$ is the level of significance.


Now from Table: \@ref(tab:Table-02), we can see that both of the variables `age` and `bmi` is significantly associated with `chol` variable.

```{r Table-02}

## ------- Code for Question-02 ------------------------

arcus <- t.test(chol ~ arcus, data = mydat) %>%
  tidy() %>%
  mutate(term = "arcus") %>%
  select(term, estimate, statistic, p.value)

mydat %>%
  select(age, bmi) %>%
  map(~ cor.test(x = .x, y = mydat$chol)) %>%
  map_dfr(broom::tidy, .id = "term") %>%
  select(term:p.value) %>%
  bind_rows(arcus) %>%
  mutate(p.value = p_format(p.value)) %>%
  kab_tab(align = "lrrr",
          caption = "Correlation Test (age, bmi) and T-test (arcus) with chol") %>%
  kable_styling(latex_options = "hold_position")

```

#### Effect of arcus:

Now to check the effect of `arcus` (a categorical variable with level 0 and 1) on `chol`, we can do two sample t-test, where one sample is people with `arcus` 0 and 
other sample is people with `arcus` 1. Therefore, is $\mu_o$ and $\mu_1$ are the 
population mean of `arcus` 0 and `arcus` 1 group respectively. 

Then our hypotheses are:
\begin{align*}
H_o&: \mu_o = \mu_1 \\
H_a&: \mu_o \neq \mu_1
\end{align*}
and appropriate test statistic (assuming unequal variance),

$$
t_o = \frac{\bar{x_o} - \bar{x_1}}{\sqrt{\frac{s_o^2}{n_o} + \frac{s_1^2}{n_1}}}
$$

where $\bar{x}$ and $s^2$ denotes sample mean and sample variance with subscript 
0 and 1 for `arcus` group 0 and 1 respectively and $n_o$ and $n_1$ are the corresponding sample sizes.

Here we will reject $H_o$ if the associated `p value` is less then  $\alpha = 0.05$, where $\alpha$ is the level of significance.

Then from Table: \@ref(tab:Table-02), since `p.value` is less than 0.001 we can conclude that mean `chol` differs significantly for 0 and 1 group of `arcus`, that is, `arcus` has significant effect on `chol`.

#### Effect of behpat:

To check the effect of `behpat` on `chol`, we can do oneway ANOVA. In this case the hypotheses are:
\begin{align*}
H_o&: \mu_1 = \mu_2 \\
H_a&: \mu_i \neq \mu_j \! &\text{for at least on i $\ne$ j}
\end{align*}
and test statistic is $F_o = \frac{MS_{reg}}{MS_{E}}$. We will reject $H_o$ if associated `p.value` is less than 0.05.


```{r Table-03}

anova(lm(chol ~ behpat, data = mydat)) %>%
  tidy() %>%
  mutate(p.value = p_format(p.value)) %>%
  kab_tab(align = "lrrrrr",
          caption = "One Way Analysis of Variance for chol on behpat") %>%
  kable_styling(latex_options = "HOLD_position")

```

Then from Table: \@ref(tab:Table-03), we conclude that mean `chol` differs significantly over the levels of `behpat`.



